### 2021-04-08 papers/SYRCoSE/regmachine-eventstruct.tex
"on fig" -> "in fig"

Let us consider an example. Given the program below, 
our semantics builds the event structure as 
shown on \cref{fig:regmachine-eventstruct-example}.

@@

On \cref{fig:eventstruct-example} one can see the prime event structure
obtained as a result of incremental construction 
depicted on \cref{fig:regmachine-eventstruct-example}.

>>>>

Let us consider an example. Given the program below, 
our semantics builds the event structure as 
shown in \cref{fig:regmachine-eventstruct-example}.

@@

In \cref{fig:eventstruct-example} one can see the prime event structure
obtained as a result of incremental construction 
depicted in \cref{fig:regmachine-eventstruct-example}.
